\documentclass[12pt]{article}

\pagestyle{empty}
\setcounter{secnumdepth}{0}

\topmargin=0cm
\oddsidemargin=0cm
\textheight=22.0cm
\textwidth=16cm
\parindent=0cm
\parskip=0.15cm
\topskip=0truecm
\raggedbottom
\abovedisplayskip=3mm
\belowdisplayskip=3mm
\abovedisplayshortskip=0mm
\belowdisplayshortskip=2mm
\normalbaselineskip=12pt
\normalbaselines

\begin{document}

\vspace*{0.2in}
\centerline{\bf\Large Diary}

\vspace*{0.2in}
\centerline{\bf\Large Name: Pavel BALAN   Student ID: 40029816}

\vspace*{0.2in}
\centerline{\bf\Large Team PK-B}

\vspace*{0.2in}
\centerline{\bf\Large 15 January 2020 and onwards}

\section{Iteration 1}

{\bf Date:} 9 January 2020\\
{\bf Start Time:} 18:30\\
{\bf End Time:} 20:45 \\
{\bf Who:} Pavel Balan, Ivan Garzon, Ki Ho Lee, Nian Liu, Anthony Menard-Gill, Michael Naccache, Ashish Saha, Myriam Tayah, Shuo Zhang\\
{\bf Where:} Lecture hall H-920 \\
{\bf Activities:} Contact info gathering, first organizational meeting from 20:15 onward.\\
{\bf Outcomes:} Slack channel Comp 354 PK-B created. Github repository for the project created.\\

{\bf Date:} 15 January 2020\\
{\bf Start Time:} 19:15\\
{\bf End Time:} 20:45 \\
{\bf Who:} Pavel Balan, Ivan Garzon, Ki Ho Lee, Nian Liu, Anthony Menard-Gill, Michael Naccache, Ashish Saha, Myriam Tayah, Mona Shayvard\\
{\bf Where:} Computer lab H-831 \\
{\bf Activities:} Meeting number 1. Went over the talking points proposed over the course of Week 1, split responsibilities along the team, ensured we are all on the same page. Use case ideas generated, one per coder. Minutes taken in Google Docs.\\
{\bf Outcomes:} Responsibilities and roles have been delegated; Slack day(day for online sharing of progress) set to Friday; Ashish Saha entrusted with teaching LaTeX to the masses; Myriam Tayah volunteered to create a JUnit primer as part of her responsibility to spread unit-testing knowledge; Ivan Garzon entrusted with implementing a Trello board for the team. All team is to learn JUnit and to have a diary by 20 January 2020.\\

{\bf Date:} 15 January 2020\\
{\bf Start Time:} 21:10\\
{\bf End Time:} 22:30 \\
{\bf Who:} Pavel Balan\\
{\bf Where:} At home \\
{\bf Activities:} Organized the Github repo; began writing a personal diary. Disseminated information about professor's site update into the Slack channel.\\
{\bf Outcomes:} A diary and a folder structure in the repository. Hopefully the template will help others to write diaries as well.\\

{\bf Date:} 16 January 2020\\
{\bf Start Time:} 20:15\\
{\bf End Time:} 20:30 \\
{\bf Who:} Pavel Balan, Michael Naccache\\
{\bf Where:} De Maisonneuve street, non-specific sandwich cafe\\
{\bf Activities:} Discussed project pace, verified way forward is smooth and there is no blockages as seen from Michael's perspective.\\
{\bf Outcomes:} A better understanding of the potential pain-points that may arise. Better knowledge about current initiatives witin the documentation team.\\

{\bf Date:} 16 January 2020\\
{\bf Start Time:} 20:30\\
{\bf End Time:} 21:20 \\
{\bf Who:} Pavel Balan, Ivan Garzon, Ki Ho Lee, Nian Liu, Anthony Menard-Gill, Michael Naccache, Ashish Saha, Myriam Tayah, Mona Shayvard\\
{\bf Where:} Lecture room H-523 \\
{\bf Activities:} Attended the tutorial. Developed existing use case ideas, generated new ones for the documentation.\\
{\bf Outcomes:} A knowledge of the UML domain model on the team's end. Team armed with a clearer understanding of the task at hand.\\

{\bf Date:} 17 January 2020\\
{\bf Start Time:} 18:05\\
{\bf End Time:} 21:40 (intermittently) \\
{\bf Who:} Pavel Balan, Ivan Garzon, Ki Ho Lee, Nian Liu, Anthony Menard-Gill, Ashish Saha; Michael Naccache, Myriam Tayah, Mona Shayvard as spectators\\
{\bf Where:} Slack channel \\
{\bf Activities:} Weekly discussion of project status online. Team checked in, reported on current progress and shared plans for the next few days.\\
{\bf Outcomes:} Check-in completed successfully. A JUnit workshop, led by Myriam Tayah, has been conducted among the coding team. The documentation team plans to begin drafting on 18 January, the coding team has a meeting on 20 January after which they begin implementation.\\

{\bf Date:} 18 January 2020\\
{\bf Start Time:} 20:30\\
{\bf End Time:} 22:30 \\
{\bf Who:} Pavel Balan\\
{\bf Where:} At home \\
{\bf Activities:} Writing supplementary organizer documentation for posterity and personal reference.\\
{\bf Outcomes:} "Primer on the organizer role in the COMP354 PK-B team" document created.\\

{\bf Date:} xxx\\
{\bf Start Time:} xxxx\\
{\bf End Time:} xxxx \\
{\bf Who:} xxx,xx,xxx (fullnames)\\
{\bf Where:} xxxx \\
{\bf Activities:} xxxxxxx\\
{\bf Outcomes:} xxxxx\\

%\section{Iteration 2}

%\section{Iteration 3}

\end{document}
